### 2018-10-15 README.Rmd
readme update

## Basic Use

The following showcases the capabilities of `areal` given that the source and target data

>>>>

## General Use

The following showcases the capabilities of `areal` given that the source and target data are loaded in by the user alongside the package dependencies. The data is hypothetical and named "source" and "target" respectively.

```r
# load the areal package
library(areal)

# generate result of SF comparison test
sf_result <- aw_validate_sf(source, target)

# generate result of unit comparision test
units_result <- aw_validate_units(source, target)

# generate result of coordinate test
crs_result <- aw_validate_crs(source,target)

# generate complete result of validation checks
validate_result <- aw_validate_data(source,target)

# intersect source and target shapefiles and generate
# geometric area
intersection <- aw_intersect(source, target)

# aggregate geometric area by source ID
intersection <- aw_total_id_area(intersection)

# create source area weight field
intersection <- aw_area_wght(intersection)

# create new interest variable based on area weight
intersection <- aw_popnew(intersection)

# aggregate new interest variable to target ID
final_target <- aw_aggregate(intersection)
```

## Use Collective Function

All of the main functions' tasks can be performed in the encompassing function `aw_interpolate()`. Its use can be seen as follows:

```r
aw_interpolate(source, target, intersection)
```

## Additional Documentation

See the package websites and vignettes. The help files can be viewed within R:

```r
?aw_interpolate
```

## About the Authors

Charlie Revord was the chef man of this package.

Christopher Prener, Ph.D. contributed to the development of this package. He is a jedi master.
